Demystifying the Computer Science PhD Admission\\in US Universities\\{\large A Guide for International Students

### 2023-11-07 demystify.tex
updates

\usepackage[T1]{fontenc}
\usepackage[margin=1.2in]{geometry}
\usepackage{soul}
%\usepackage[small,compact]{titlesec} %very powerful
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{epigraph}
\usepackage{cite}
\usepackage{caption}
\captionsetup{font=small}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{wrapfig}
\setlength\intextsep{0pt} % remove extra space above and below in-line float
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=blue,
}
\usepackage{booktabs}

@@

\title{Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students}}

\author{\href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen} (\href{mailto:tvn@gmu.edu}{tvn@gmu.edu})\\{\small George Mason University, Dept. of Computer Science}}

\begin{document}
\frontmatter

\maketitle
\chapter{Preface}
Having been involved in PhD admissions for many years, I've
realized that many \textbf{international students}, especially those from smaller countries like Vietnam, lack a clear understanding of
the Computer Science PhD admission process at US universities. This confusion not only
discourages students from applying but also creates the perception that
getting admitted to a CS PhD program in the US is difficult compared to other countries.

@@

\section{Difference between PhD in the US and other countries}\label{sec:non-us-differences}
Here we summarize the main differences between CS PhD in the US and other countries.  This is based on my experience and what I heard from others who did PhD in other countries.

@@

\section{How do I address a professor?}\label{sec:address}

      \begin{center}
        \includegraphics[scale=0.7]{c5.png}
      \end{center}

>>>>

\usepackage[T1]{fontenc}
\usepackage[margin=1.5in]{geometry}
\usepackage{soul}
%\usepackage[small,compact]{titlesec} %very powerful
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{epigraph}
\usepackage{cite}
\usepackage{caption}
\captionsetup{font=small}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{wrapfig}
\setlength\intextsep{0pt} % remove extra space above and below in-line float
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=blue,
}
\usepackage{booktabs}

@@

\title{Demystifying the Computer Science PhD Admission\\in US Universities\\{\large A Guide for International Students}}

\author{\href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen}\\{\small George Mason University, Dept. of Computer Science}}

\chapterstyle{pedersen}

\makeatletter
\def\maketitle{%
  \null
  \thispagestyle{empty}%
  \vfill
  \begin{center}\leavevmode
    \normalfont
    {\LARGE\raggedright \@title\par}%
    \vfill%
    %\hrulefill\par
    {\Large \@author\par}%
    \vfill%
    {\large\raggedleft \@date\par}%
  \end{center}%
  \vfill
  \null
  \cleardoublepage
  }
\makeatother
%\author{ThanhVu H. Nguyen}
%\title{TITLE OF BOOK}
%\date{}

\begin{document}
\maketitle
\frontmatter

\chapter{Preface}
Having been involved in PhD admissions for many years, I've
realized that many \textbf{international students}, especially those from smaller countries like Vietnam, lack a clear understanding of
the Computer Science PhD admission process at US universities. This confusion not only
discourages students from applying but also creates the perception that
getting admitted to a CS PhD program in the US is difficult compared to other countries.

@@

\section{Differences between PhD in the US and other countries}\label{sec:non-us-differences}
This summarizes the main differences between CS PhD in the US and other countries. % This is based on my experience and what I heard from others who did PhD in other countries.

@@

\section{How do I call or address a professor?}\label{sec:address}

\begin{center}
\includegraphics[scale=0.6]{c5.png}
\end{center}
